Rmarkdown Features

### 2018-04-03 Instructions/Rmarkdown_features/rmd_features.rmd
update

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev='svg'
)
```

@@

$\LaTeX$ Rendering {.tabset}
-----------------------------
### Passing Matrix Object

@@

1. success
2. warning
3. warning
4. error

```{html}
<div class="error">
some text in the colored region
</div>
```

<div class="error">
some text in the colored region
</div>

>>>>

---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: Apr 3, 2018
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
```

About This Document {.tabset}
-----------------------------
### yaml of this Doc
```yaml
---
title: "Rmarkdown Features"
subtitle: "This is subtitle"
author: Yongfu Liao
date: March 18, 2018
bibliography: /Users/user/local_depend/citation/neanderthals.bib
csl: /Users/user/local_depend/style_sheets/apa-no-doi-no-issue.csl
link-citations: yes
output:
  html_document:
    code_folding: show
    css: /Users/user/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 4
    toc_float: true
---
```

PDF Document (Chinese) {.tabset}
-----------------------------

### yaml

```yaml
---
output:
  pdf_document:
    latex_engine: xelatex    
    includes:
        in_header: header.tex
documentclass: article
urlcolor: "blue"
fontsize: 12pt
---
```

### header.tex
```tex
%加這個就可以設定字體
\usepackage{fontspec}
%使用xeCJK，其他的還有CJK或是xCJK
\usepackage{xeCJK}

%設定英文字型，不設的話就會使用預設的字型
\setmainfont{Calibri}

%設定中英文的字型
%字型的設定可以使用系統內的字型，而不用像以前一樣另外安裝
\setCJKmainfont{蘋方-繁}

%中文自動換行
\XeTeXlinebreaklocale "zh"

%文字的彈性間距
\XeTeXlinebreakskip = 0pt plus 1pt

%設定段落之間的距離
\setlength{\parskip}{0.15cm}

%設定行距
\linespread{1.2}\selectfont
```

@@

$\LaTeX$ Math Rendering {.tabset}
-----------------------------
### Passing Matrix Object

@@

1. success
2. warning
3. info
4. error

```{html}
<div class="info">
some text in the colored region
</div>
```

<div class="info">
some text in the colored region
</div>

#### Bootstrap Alert

Alternatively, you can use bootstrap's default alert divs, defined by four classes:

1. alert-success
2. alert-warning
3. alert-info
4. alert-danger
```{html}
<div class="alert alert-success">
some text in the colored region
</div>
```

<div class="alert alert-success">
Bootstrap-defined colored region
</div>
